### 2016-11-14 paper/intro.tex
pass on intro; move text to related work

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, which can lead to late reports of test
failures.  At large IT companies (e.g.,
Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
common problem .  \Mar{Ask Milos if he can share stories on how
  prevalent regression testing is at Microsoft and Google, if he can
  explain how they run tests, and how prevalent is parallelization (in
  contrast to regression testing).}

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  To that end
Ekstazi analyzes, for each test, which test-dependent files have
changed.

%; these
%dependencies are computed and maintained at low cost.

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.
For large IT organizations, the alternative of renting server farms,
or even building one, is a potential escape to the regression testing
problem.  However, for open-source projects and for projects of
smaller organizations with lower budgets for building testing
infrastructures, this alternative is not as attractive.

@@

Motivated by this potential gap in regression testing practice, we
first studied (1) how prevalent long-running test suites are in
open-source software projects.  To conduct this experiment we selected
\numSubjs{} Java projects from github that are highly-popular and use
the Maven build system.  (Section~\ref{sec:eval} details our selection
methodology.)  Our experimental results indicate that long-running
test suites (taking longer than 5m to complete\Fix{check if Ekstazi
  paper also used this value and cite}) are not
rare~--~\numLongRunning{} of the projects we analyzed contain
long-running test suites.  From this result we investigated (2) how
frequently the projects we considered use parallelization to speedup
test runs.  We parsed build files of projects to identify usage of
parallelism. \Mar{justify parallelization}.  Our results indicate that
\percentParallelForLongRunning{} of long-running test suites do use
parallelism to speedup execution.  Given the popularity of this
solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the effects of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related with parallelization that could justify
adoption resistance.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  At large IT organizations, dealing with high
testing costs is a common problem.  The Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} provide evidence about
the importance of speeding up test execution in industry.  This
problem is not specific for giants like Microsoft and Google; it also
occur in other domains.  For example, a recent paper from the
automotive industry reported that test suites can take days to
run~\cite{artl-etal-icst2015}.

%% papers also indicate the important of speeding up the testing process
%% in other industrial domain, e.g., in 
%% \Mar{Ask Milos if he can share stories on how prevalent regression
%%   testing is at Microsoft and Google, if he can explain how they run
%%   tests, and how prevalent is parallelization (in contrast to
%%   regression testing).}

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem in academia and at large organizations, to the
best of our knowledge no prior work has investigated how prevalent the
problem is in open-source projects.  In large organizations, the
alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}}, or even building a
server farm (for increased security), is a potential escape to the
regression testing problem.  Considering open-source projects and
lower-budget projects, the alternative of building or using high-end
infrastructures is not as attractive but it is unclear how relevant
regression testing is in this scenario.

@@

Motivated by this potential gap in regression testing, we studied (1)
how prevalent long-running test suites are in open-source software
projects.  To conduct this experiment we selected \numSubjs{} Java
projects from github that are highly-popular and use the Maven build
system.  (Section~\ref{sec:eval} details our selection methodology.)
Our experimental results indicate that long-running test suites
(taking longer than 5m to complete\Fix{check if Ekstazi paper also
  used this value to indicate long runs and cite}) are not
rare~--~\numLongRunning{} of the projects we analyzed contain
long-running test suites.  \Mar{missing connection. why parallelism?}
From this result we investigated (2) how frequently the projects we
considered use parallelization to speedup test runs.  Our results
indicate that \percentParallelForLongRunning{} of long-running test
suites do use parallelism to speedup execution.  Given the popularity
of this solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the benefits of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related to parallelization that could justify adoption
resistance.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild
